\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{4pt}{2pt}
\setlist[itemize]{noitemsep, topsep=1pt, partopsep=0pt, parsep=0pt, itemsep=1.2pt, leftmargin=12pt}
\hypersetup{colorlinks=true, urlcolor=blue}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \bfseries BODDEPALLI LAXMANA RAO} \\
    \vspace{2pt}
    Hyderabad, India | DOB: 28-05-2002 | +91 8367027220 | \href{mailto:laxmana.dev@gmail.com}{laxmana.dev@gmail.com} \\
    \href{http://linkedin.com/in/boddepalli-laxmanarao/}{linkedin.com/in/boddepalli-laxmanarao} | \href{https://github.com/laxmanarao5}{github.com/laxmanarao5} | \href{https://laxman-dev.vercel.app}{laxman-dev.vercel.app}
\end{center}
\vspace{4pt}
% --- CAREER OBJECTIVE ---
\section{Career Objective}
Result-oriented Fullstack Developer seeking a Senior role to leverage 3.5 years of expertise in Next.js/React frontends, Node.js GraphQL gateways, and Python microservices. Committed to architecting scalable cloud solutions, streamlining DevOps workflows, and driving engineering excellence in high-impact software environments.

% --- SKILLS ---
\section{Key Skills}
\begin{itemize}
    \item \textbf{Backend:} Node.js (Express, Apollo Server), Python (Django, Flask), RESTful APIs, GraphQL Gateway, Microservices Architecture
    \item \textbf{Frontend:} React.js, Next.js, TypeScript, JavaScript (ES6+), Redux Toolkit, HTML5/CSS3, Responsive UI
    \item \textbf{Cloud \& DevOps:} Azure, AWS (EC2, S3, Lambda, CloudFront), Docker, Kubernetes, CI/CD (Azure DevOps, GitHub Actions, AWS CodeBuild)
    \item \textbf{Databases:} PostgreSQL, MySQL, SQL Server, DynamoDB, MongoDB, Redis
    \item \textbf{AI & Tooling:} OpenAI API, Claude/Anthropic APIs, AWS Bedrock, Git
    \item \textbf{Observability \& Testing:} Jest, PyTest, Postman, CI/CD Automation
\end{itemize}

% --- ACHIEVEMENTS ---
\section{Key Achievements}
\begin{itemize}
    \item Migrated Next.js frontend and Node.js GraphQL gateway from Node 20 to Node 24, upgrading core dependencies, reducing build times by 20\%, and patching legacy CVEs.
    \item Refactored high-latency Python report-generation microservice utilizing ThreadPool parallelization and batch SQL inserts, reducing processing time from 60+ minutes to under 60 seconds.
    \item Automated 1M+ record migration to Azure using robust pipelines with zero manual reconciliation, saving 2--3 hours daily.
    \item Designed Apollo Server GraphQL gateway in Node.js to replace REST endpoints, optimizing payload size and client data retrieval.
\end{itemize}

% --- EXPERIENCE ---
\section{Professional Experience}
\textbf{Software Engineer (Fullstack)} | \textbf{Veltris}, Hyderabad \hfill \textit{Feb 2023 -- Present}
\begin{itemize}
    \item Architected responsive Next.js/React frontends and Node.js GraphQL API gateway layers; led migration of web client and API layers from Node 20 to Node 24 for enhanced stability.
    \item Built and maintained Python report microservices and Node.js GraphQL schemas supporting optical fiber manufacturing and hardware testing workflows.
    \item Designed and optimized Azure-based CI/CD pipelines, automating deployments and decreasing deployment times from 8 minutes to 1.5 minutes using Docker caching.
    \item Wrote unit and integration test suites using Jest and PyTest, maintaining 85\%+ test coverage for web clients and microservices.
\end{itemize}

% --- PROJECTS ---
\section{Projects}
\textbf{AFL Global -- Fiber Testing Web Suite} \hfill \textit{Next.js, Node.js, GraphQL, Python Microservices}
\begin{itemize}
    \item Managed Next.js frontend, GraphQL gateway, and Python reporting microservice for a web suite interfacing with a .NET hardware testing engine.
    \item Led the codebase upgrade from Node 20 to Node 24, upgrading Apollo Client/Server, resolving dependency conflicts, and improving compilation performance.
    \item Optimized a high-latency Python reports microservice using parallel execution and database batch inserts, reducing report generation times by 60x (from 60+ minutes to under 60 seconds).
    \item Created unified GraphQL schemas and resolvers on Apollo Server, replacing fragmented REST endpoints and minimizing data payload over-fetching by 40\%.
\end{itemize}

\textbf{Olivet Migration -- Data Platform} \hfill \textit{Node.js, Azure, SQL, Azure DevOps}
\begin{itemize}
    \item Built a high-throughput, fault-tolerant migration tool using Node.js to transfer 1M+ records to Azure SQL with automated validation and rollback support.
\end{itemize}

\textbf{Serverless Finance Manager} \hfill \textit{Flask, React.js, TypeScript, AWS Lambda, CloudFront}
\begin{itemize}
    \item Developed a serverless ledger application using AWS Lambda, CloudFront, a React/TypeScript frontend, and a Flask backend with DynamoDB storage.
\end{itemize}

% --- EDUCATION ---
\section{Education}
\textbf{Rajiv Gandhi University of Knowledge Technologies (RGUKT)}, Srikakulam \hfill \textit{2019 -- 2023}
\begin{itemize}
    \item Bachelor of Technology in Computer Science \& Engineering | CGPA: 8.7/10
\end{itemize}

\end{document}